---
title: "introductionRmarkdown"
author: "Stijn Hanssen"
date: "22/07/2020"
output: html_document
---

## R Markdown

```{r, include=FALSE}
# Install Python environment 
library(reticulate)
reticulate::install_miniconda()
```

## Chunck Options

* include = FALSE prevents code and results from appearing in the finished file. R Markdown still runs the code in the chunk, and the results can be used by other chunks.

* echo = FALSE prevents code, but not the results from appearing in the finished file. This is a useful way to embed figures.

* message = FALSE prevents messages that are generated by code from appearing in the finished file.

* warning = FALSE prevents warnings that are generated by code from appearing in the finished.

* fig.cap = "..." adds a caption to graphical results.

To set global options that apply to every chunk in your file, call knitr::opts_chunk\$set in a code chunk. Knitr will treat each option that you pass to knitr::opts_chunk\$set as a global default that can be overwritten in individual chunk headers

```{r, include=FALSE}
x <- 10
```

## Inline code

R Markdown will always
* display the results of inline code, but not the code
* apply relevant text formatting to the results


`r y = x+x `

```{r}
y
```

## Code languages

```{python}
print('"Isn\'t," they said.')
```

