---
title: "introductionRmarkdown"
author: "Stijn Hanssen"
date: "22/07/2020"
output: html_document
bibliography: references.bib
params:
    data: "hawaii"
---

## R Markdown

```{r, include=FALSE}
# Install Python environment 
library(reticulate)
# reticulate::install_miniconda()
library(knitr)
```

## Chunck Options

* include = FALSE prevents code and results from appearing in the finished file. R Markdown still runs the code in the chunk, and the results can be used by other chunks.

* echo = FALSE prevents code, but not the results from appearing in the finished file. This is a useful way to embed figures.

* message = FALSE prevents messages that are generated by code from appearing in the finished file.

* warning = FALSE prevents warnings that are generated by code from appearing in the finished.

* fig.cap = "..." adds a caption to graphical results.

To set global options that apply to every chunk in your file, call knitr::opts_chunk\$set in a code chunk. Knitr will treat each option that you pass to knitr::opts_chunk\$set as a global default that can be overwritten in individual chunk headers.

```{r, include=FALSE}
x <- 10
```

## Inline code

R Markdown will always:
* display the results of inline code, but not the code
* apply relevant text formatting to the results


`r y <- x+x `

```{r}
# y <- x+x (y = incline code, x = include=FALSE)
y
```

## Code languages

```{python}
# Python code
print('"Isn\'t," they said.')
```

## Parameters
Parameters are declared using the params field within the YAML header of the document (at the top; params: data: "...").

To access a parameter in code, call params$<parameter name>

```{r}
# render("5-parameters.Rmd", params = list(data = "aleutians"))
# data(list = params$data)
```

## Tables

```{r, echo=FALSE, results= 'asis'}
kable(mtcars[1:5,], caption = "A knitr kable.")
```

## Markdown Basics

- *italics*
- **bold**
- `code`
- superscript^2^
- ~~strikethrough~~
- [links](rmarkdown.rstudio.com)
- Latex equations $E = mc^{2}$
- And bibliographies [@R-base]

## Output Formats

You can create many types of output from a single .Rmd file. R Markdown has built in support for **HTML, PDF, MS_Word, ODT, RTF, Markdown, and Github flavored Markdown documents; Beamer, slidy.js, ioslides, and reveal.js slideshows; and websites, dashboards, books, handouts, package vignettes, and Shiny apps**.

Use define setting section to change the output, each output can include params.



